---
title: "BA Assignment 2"
author: "VINAY KACHARAM"
date: "2023-10-16"
output:
  html_document: default
  word_document: default
  pdf_document: default
---


#Loading the Dataset :

```{r}
setwd("C:/Users/vinay/OneDrive/Desktop/BA R PRO/")
dataframe=read.csv("C:/Users/vinay/OneDrive/Desktop/BA R PRO/Online_Retail.csv")
```
## Loading the library(dplyr)
```{r}
library(dplyr)
```

## 1.Showing how many transactions are in the dataset for each country :

```{r}
Total_trans=nrow(dataframe)
Total_trans
```

```{r}
Tran_count <- dataframe %>% group_by(Country) %>% summarize(Count = n())
Tran_count
```
This is the number of transactions for each country.

#Now Calculate the percentage of the transactions for each country :
```{r}
country_count_Per <- Tran_count %>% mutate(Percentage = (Count / Total_trans) * 100)
country_count_Per
```
This is the percentage of the transactions for each country

#Now Show the countries with more the 1% of total transactions:
```{r}
country_counts_filter <- country_count_Per %>% filter(Percentage > 1)
country_counts_filter 
```

## 2.Creating a new variable "TransactionValue" by multiplying "Quantity" and "UnitPrice":
```{r}
dataframe$TransactionValue <- dataframe$Quantity*dataframe$UnitPrice
head(dataframe)
```

## 3.Showing the breakdown of transaction values by countries:
```{r}
country_totals <- dataframe %>% group_by(Country) %>% summarize(TotalValue = sum(TransactionValue))
country_totals
```

#Display only countries with total transaction exceeding 130,000 British Pounds:
```{r}
filtered_countries <- country_totals %>% filter(TotalValue > 130000)
filtered_countries
```
## 4.We are dealing with the InvoiceDate variable: printing the time, date, day of week, month, converting the datatypes of the following as mentioned in the assignment.

```{r}
Temp=strptime(dataframe$InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT')
head(Temp)
```
```{r}
dataframe$New_Invoice_Date <- as.Date(Temp)
head(dataframe$New_Invoice_Date)
```

```{r}
dataframe$New_Invoice_Date[20000]- dataframe$New_Invoice_Date[10]
```

```{r}
dataframe$Invoice_Day_Week= weekdays(dataframe$New_Invoice_Date)
head(dataframe$Invoice_Day_Week)
```

```{r}
dataframe$NewInvoice_Hour = as.numeric(format(Temp, "%H"))
head(dataframe$NewInvoice_Hour)
```

```{r}
dataframe$New_Invoice_Month = as.numeric(format(Temp, "%m"))
head(dataframe$New_Invoice_Month)
```

##(a)
Show the percentage of transactions by days of the week

```{r}
weekday_count = dataframe %>% group_by(Invoice_Day_Week) %>%
summarise(percent = 100* n()/nrow(dataframe))
weekday_count
```

##(b)
Show the percentage of transactions (by transaction volume) by days of the week 
```{r}
weekdays_sum = dataframe %>% group_by(Invoice_Day_Week) %>% summarise(sum=sum(TransactionValue))
weekdays_sum_per = 100*(weekdays_sum$sum)/sum(weekdays_sum$sum)
weekdays_sum$sum = weekdays_sum_per
weekdays_sum
```
##(c)
Show the percentage of transactions (by transaction volume) by month of the year 
```{r}
Invoice_per_month = dataframe %>% group_by(New_Invoice_Month) %>% summarise(sum=sum(TransactionValue))
Month_per = 100*(Invoice_per_month$sum)/sum(Invoice_per_month$sum)
Invoice_per_month$sum = Month_per
Invoice_per_month
```
##(d)
The highest number of transactions from Australia with date
```{r}
Australia_trans = dataframe %>% filter(Country == "Australia") %>% group_by(New_Invoice_Date) %>% summarise(total=n())
Aus_Max_trans_dt = Australia_trans[which.max(Australia_trans$total),]
Aus_Max_trans_dt
```


## 5.Plot the histogram of transaction values from Germany:
```{r}
Trans_germ=dataframe[dataframe$Country=="Germany",]
Tranval_germ=Trans_germ$TransactionValue

hist(Tranval_germ,main="Histogram of Transaction values from Germany",xlab="Transaction Value",ylab="Frequency",col="orange",border="black")
```

## 6.Find Which customer had the highest number of transactions :
```{r}
no_of_trans=table(dataframe$CustomerID)
High_no_of_trans=names(which.max(no_of_trans))
High_no_of_trans
```

#Find the most valuable customer i.e.,the customer with highest total sum of transactions:
```{r}
sum_trans_cust <- tapply(dataframe$TransactionValue, dataframe$CustomerID, sum)
most_val_cust <- names(which.max(sum_trans_cust))
print(most_val_cust)
```

## 7.Calculate the percentage of missing values for each variable in the dataset:
```{r}
NA_per = colMeans(is.na(dataframe))*100
NA_per
```

## 8.The number of transactions with missing CustomerID records by countries :
```{r}
NA_Cust = dataframe[is.na(dataframe$CustomerID),]
table(NA_Cust$Country)
```

## 9.the costumers comeback to the website for their next shopping

```{r}
Come_back <- table (dataframe$Invoice_Day_Week,dataframe$New_Invoice_Date)
Come_back_New<- diff(Come_back)
mean(Come_back_New)
```
## 10.Calculate The return rate for the French customers:
```{r}
Fren_cust = filter(dataframe,Country=="France" )
Rate_return = nrow(filter(Fren_cust,Quantity<1))/nrow(Fren_cust)
Rate_return
```

## 11.The product that has generated the highest revenue for the retailer:
```{r}
Highreve_product= dataframe %>% group_by(StockCode) %>% summarise(Sum_trnsval = sum(TransactionValue))
Highreve_product[which.max(Highreve_product$Sum_trnsval),]
```

## 12. The unique customers are represented in the dataset:
```{r}
length(unique(dataframe$CustomerID))
```
